Semi-permeable vesicles: mathematical formulation, numerics and physics

### 2019-03-19 vesicle_code/docs/permeableVes/main.tex
making changes to semi-permeable writeup
updated semipermeable writeup

\section{Integral equation formulation}
There are multiple ways to convert the PDE problem into integral equations. Based on my derivation, the coupled set of integro-differential equations satisfy the given interfacial conditions:
\beq \dot{\mbx} = \mbu_\infty(\mbx) + \beta (\mbf_\text{mem}\cdot\mbn)\mbn + \sgl [\mbf_\text{mem}], \eeq
\beq \mbx_s\cdot\dot{\mbx}_s = 0 \eeq
This satisfies all the jump conditions. As usual, $\sgl$ is the single layer potential. 
\end{document}

>>>>

\section{Integral equation formulation}
There are multiple ways to convert the PDE problem into integral
equations. Based on my derivation, the coupled set of
integro-differential equations satisfy the given interfacial conditions:
\beq 
  \dot{\mbx} = \mbu_\infty(\mbx) + \beta (\mbf_\text{mem}\cdot\mbn)\mbn + \sgl [\mbf_\text{mem}], 
  \label{eqn:vesVelocity}
\eeq
\beq 
  \mbx_s\cdot\dot{\mbx}_s = 0 
\eeq
This satisfies all the jump conditions. As usual, $\sgl$ is the single layer potential.

\section{Numerics}
To address stiffness associated with high-order derivatives,
equation~\eqref{eqn:vesVelocity} is discretized with a semi-implicit
time stepping method similar to our previous works.  First, we introduce
the notation
\begin{align}
  \BB[\mbx]\mbf &= \frac{d^4}{ds^4} \mbf, \\
  \TT[\mbx]\sigma &= (\sigma \mbx_s)_s, \\
  \PP[\mbx]\mbf &= (\mbf \cdot \mbn) \mbn, \\
  \dbl[\mbx]\mbf &= \mbx_s \cdot \mbf_s
\end{align}
where $\mbn$ is the is the outward unit normal of the vesicle
parameterized by $\mbx$, and $d/ds$ is its arclength derivative.
Dropping the dependence of the operators on $\mbx$, the dynamics of the
vesicle are governed by
\begin{align}
  \dot{\mbx} &= \mbu_{\infty}(\mbx) + 
  \beta \PP(\BB\mbx + \TT\sigma) + \sgl(\BB\mbx + \TT\sigma), \\
  \dbl \dot{\mbx} &= 0.
\end{align}
Using the notation $\BB^N$ to denote the bending operator due to the
vesicle configuration at time $t_N$, and similar notation for the other
operators, we apply the semi-implicit time
\begin{multline}  
  \frac{\mbx^{N+1} - \mbx^N}{\Delta t} = \mbu_\infty(\mbx^N) 
  + \beta \PP^N(\BB^N\mbx^{N+1} + \TT^N\sigma^{N+1})  \\
  + \sgl^N(\BB^N\mbx^{N+1} + \TT^N\sigma^{N+1}).
\end{multline}
Applying $\dbl$ to the first-order time discretization of
equation~\eqref{eqn:vesVelocity}, the inextensibility condition is
\begin{align*}
  &\dbl^N(\mbx^{N+1} - \mbx^N) = 0 \\ 
  \Rightarrow &\dbl^N\mbx^{N+1} = \dbl^N \mbx^N \\ 
  \Rightarrow &\dbl^N\mbx^{N+1} = 1.
\end{align*}
Finally, we write the time stepping method in matrix form as
\begin{align}
  A \left(
    \begin{array}{c}
      \mbx^{N+1} \\ \sigma^{N+1}
    \end{array}
  \right) = 
  \left(
    \begin{array}{c}
      \mbx^{N} + \Delta t \mbu_\infty(\mbx^N) \\ \mathbf{1}
    \end{array}
  \right),
\end{align}
where
\beq
 A = \left(
  \begin{array}{cc}
    I - \Delta t \beta \PP^N - \Delta t \sgl^N \BB^N & 
    -\Delta t \PP^N \TT^N - \Delta t \sgl^N \TT^N \\
    \dbl^N & 0
  \end{array}
  \right)
\eeq

%We obtain the matrix
%\begin{multline}
% \begin{pmatrix}
% 	\mbx^N \\ \textbf{1} 
% \end{pmatrix} = \\
%\begin{pmatrix}
%	I - \Delta t \sgl^N\mathcal{B}^N - \Delta t \beta \mathcal{P}^N\mathcal{B}^N & -\Delta t \sgl^N \mathcal{T}^N-\Delta t\beta \mathcal{P}^N\mathcal{T}^N \\ & \textbf{0}
%\end{pmatrix}
%\begin{pmatrix}
%	\mbx^{N+1} \\ \sigma^{N+1}
%\end{pmatrix} 
%\end{multline}

\end{document}
